Model Checking Differentially Private Properties

### 2018-01-30 specifications.tex
spec

As an example, for our threshold \lz{to do} model, we consider the property $\wedge_{i=1}^{c} \dpriv{\epsilon}{0}(\X^k \top) \wedge \PJ{\le 10^{-6}}(\X^c F T) \wedge \dpriv{\epsilon}{0}(\X^c F \top)$.
that is used to express the privacy for our threshold Markov chains. It is only a valid formula if we would allow infinite conjunctions. However, it is interesting to note the relation to language equivalence for probabilistic automata\lz{to be discussed}

@@

Consider the Bluetooth example in~\cite{prism-bluetooth-page} and the
formula $\dpriv{\epsilon}{\delta}{\F \G \mathit{timeout}}$. Let us say
two states are neighbors if a slave device in a state is replaced by
another device in the other state.
Then the formula holds if the probability of having
continuous time out (say, in the denial of service attack) is
$(\epsilon, \delta)$-close for all neighbors. That is, adding a slave
device cannot increase the chance of service failure significantly.

>>>>

As an example, for our threshold \lz{to do} model, we consider the property $\wedge_{i=1}^{7} \dpriv{3}{0}(\X^i \top) \wedge \PJ{\le .1}(\X^7 F T) \wedge \dpriv{3}{0}(\X^7 F \top)$.
that is used to express the privacy for our threshold Markov chains. It is only a valid formula if we would allow infinite conjunctions. However, it is interesting to note the relation to language equivalence for probabilistic automata\lz{to be discussed}

@@

Consider the Bluetooth example in~\cite{DKNP04} and the
formula $\dpriv{\epsilon}{\delta}{\F \G \mathit{timeout}}$. Let us say
two states are neighbors if a slave device in a state is replaced by
another device in the other state.
Then the formula holds if the probability of having
continuous time out (say, in the denial of service attack) is
$(\epsilon, \delta)$-close for all neighbors. That is, adding a slave
device cannot increase the chance of service failure significantly.
